---
title: "Untitled"
author: "Kiera Matiska"
date: "1/29/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(janitor)
```

## Read in data

```{r}
food_access <- read_csv("food_access_research_atlas.csv") %>% 
  clean_names()
```

Create subset with the variable :

- state
- county
- urban
- pop2010
- ohu2010
- median_family_income
- lapop1_10
- lapop05_10
- lapop1_20
- lalowi1_10
- lalowi05_20
- lalowi1_20
- lapophalf
- lalowihalf
- lawhitehalf
- lablackhalf
- laasianhalf
- lanhopihalf
- laaianhalf
- laomultirhalf
- lahisphalf
- lahunvhalf
- lasnaphalf
- lapop1
- lalowi1
- lawhite1
- lablack1
- laasian1
- lanhopi1
- laaian1
- laomultir1
- lahisp1
- lahunv1
- lasnap1
- lapop10
- lalowi10
- lawhite10
- lablack10
- laasian10
- lanhopi10
- laaian10
- laomultir10
- lahisp10
- lahunv10
- lasnap10
- lapop20
- lalowi20
- lawhite20
- lablack20
- laasian20
- lanhopi20
- laaian20
- laomultir20
- lahisp20
- lahunv20
- lasnap20
- tract_lowi
- tract_white
- tract_black
- tract_asain
- tract_nhopi
- tract_aian
- tract_o_multir
- tract_hispanic
- tract_hunv
- tract_snap

```{r}
food_access_subset <- food_access %>% 
  select(state, county, urban,
         pop2010, ohu2010, median_family_income, 
         lapop1_10, lapop05_10, lapop1_20, 
         lalowi1_10, lalowi05_10, lalowi1_20,
         lapophalf, lalowihalf, lawhitehalf,
         lablackhalf, laasianhalf, lanhopihalf,
         laomultirhalf, lahisphalf, lahunvhalf,
         lasnaphalf, lapop1, lalowi1,
         lawhite1, lablack1, laasian1,
         lanhopi1, laaian1, laomultir1,
         lahisp1, lapop10, lalowi10,
         lawhite10, lablack10, laasian10,
         lanhopi10, laaian10, laomultir10,
         lahisp10, lahunv10, lasnap10,
         lapop20, lalowi20, lawhite20,
         lablack20, laasian20, lanhopi20,
         laaian20, laomultir20, lahisp20,
         lahunv20, lasnap20, tract_lowi,
         tract_white, tract_black, tract_asian,
         tract_nhopi, tract_aian, tract_o_multir,
         tract_hispanic, tract_hunv, tract_snap)
```

## Export data subset as .csv

```{r}
write_csv(food_access_subset, file = "food_access_subset.csv")
```
